Fourmile

### 2022-09-19 fourmile_dataprocess.Rmd
adding in solar rad gap filling

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)
library(hydroGOF)
library(Metrics)
```

@@

#summary(srad_fracshift)
rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
summary(niwot_daymet_comp$diff)

>>>>

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)
library(hydroGOF)
library(Metrics)
library(ranger)
library(missRanger)
```

@@

#summary(srad_fracshift)
rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
summary(niwot_daymet_comp$diff)
```

### Solar rad gap filling

```{r}
